Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-08-28 writing/CONUS_AOD.qmd
Added a table of IVs.

>>>>

@tbl-ivs shows the distribution of each predictor in the CV.

```{r tbl-ivs}
#| tbl-cap: !expr 'sprintf("`time.sat` is represented in days since %s.", as.character(min(dt$time.sat), usetz = T))'
flextable(rbindlist(lapply(Wf$features, \(iv)
   {nv = dt[[iv]]
    v = na.omit(nv[!is.na(nv)])
    r = \(x) round(x, 3)
    if (iv == "time.sat")
        v = as.numeric(difftime(v, min(v), units = "days"))
    data.table(
        Variable = iv,
        missing = r(mean(is.na(nv))),
        min = r(min(v)),
        max = r(max(v)),
        mean = r(mean(v)),
        sd = r(sd(v)))})))
```
